\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
fix desc

From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai 3 (over 3 \textmu s) than on Xenomai 2 (below 3 \textmu s). While this is not an occasional case, we already ensured the same experiment method was ran a couple of times, we tried to look into the test code of latency to figure out the cause of this phenomenon. In user-level mode, the measurement task is carried out by the function 'latency' inside the program; whereas in kernel or irq mode, the task is executed by issuing a Xenomai RTDM command such as:
\begin{verbatim}
rt_dev_ioctl(benchdev, \
RTTST_RTIOC_INTERM_BENCH_RES,&result); 
\end{verbatim} 
in an infinite loop to periodically launch timer and capture latencies. Unfortunately, we were unable to discover the reason for the discrepancy on the observed data at that time.

@@

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2. However, comparing to Xenomai 2, our results show the unexpected slowdown of timer interrupt hanlding latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though. It is not clear why Cobalt in Xenomai 3 contributes to larger interrupt jitter measurement when the CPU is heavily loaded. This needs further investigation.

>>>>

From the data above, it shows that the latency performance of timer-irq in CPU-STRESSED situation is slightly worse on Xenomai 3 (over 3 \textmu s) than on Xenomai 2 (below 3 \textmu s). While this is not an occasional case, we already ensured the same experiment method was ran a couple of times, we tried to look into the test code of latency to figure out the cause of this phenomenon. In user-level mode, the measurement task is carried out by the function 'latency' inside the program; whereas in kernel or irq mode, the task is executed by issuing a Xenomai RTDM operation such as:
\begin{verbatim}
rt_dev_ioctl(benchdev, \
RTTST_RTIOC_INTERM_BENCH_RES,&result); 
\end{verbatim} 
in an infinite loop to periodically launch timer and capture latencies. Unfortunately, we were unable to discover the reason for the discrepancy on the observed data at that time.

@@

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2. However, comparing to Xenomai 2, our results show the unexpected slowdown of timer interrupt hanlding latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though. It is not clear why Cobalt in Xenomai 3 contributes to larger interrupt jitter when the CPU is heavily loaded. This needs further investigation.
